The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
A word
A word; synced hash

\IfFileExists{vc.tex}{\input{vc.tex}}{\newcommand{\githash}{db0ab84}\newcommand{\giturl}{https://www.github.com/AnnieJumpCannon/rave}}

@@

\begin{abstract}
The orbits, atmospheric parameters, chemical abundances, and ages of 
individual stars in the Milky Way provide the most comprehensive 
illustration of galaxy formation available.  The Tycho-\gaia\ 
Astrometric Solution (\tgas) will deliver astrometric parameters for
the largest ever sample of Milky Way stars, though its full potential
cannot be realized without the addition of complementary spectroscopy.  
Among existing spectroscopic surveys, the RAdial Velocity Experiment 
(\rave) has the largest overlap with \tgas\ ($\gtrsim$200,000 stars).  
We present a data-driven re-analysis of \Nspectra\ \rave\ spectra using 
\thecannon.  For red giants, we build our model using high-fidelity 
\apogee\ stellar parameters and abundances for stars that overlap 
with \rave.  For main-sequence and sub-giant stars, our model uses 
stellar parameters from the \epic.  We derive and validate 
effective temperature $\teff$, surface gravity $\logg$, and chemical 
abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni).  We 
report a total of \ReportedAbundances\ elemental abundances with a 
typical precision of 0.07~dex, a substantial improvement over past 
\rave\ data releases.  The synthesis of \raveon\ and \tgas\ is the 
most powerful data set for chemo-dynamic analyses of the Milky Way ever produced.
\end{abstract}

>>>>

\IfFileExists{vc.tex}{\input{vc.tex}}{\newcommand{\githash}{794a221}\newcommand{\giturl}{https://www.github.com/AnnieJumpCannon/rave}}

@@

\begin{abstract}
The orbits, atmospheric parameters, chemical abundances, and ages of 
individual stars in the Milky Way provide the most comprehensive 
illustration of galaxy formation available.  The Tycho-\gaia\ 
Astrometric Solution (\tgas) will deliver astrometric parameters for
the largest ever sample of Milky Way stars, though its full potential
cannot be realized without the addition of complementary spectroscopy.  
Among existing spectroscopic surveys, the RAdial Velocity Experiment 
(\rave) has the largest overlap with \tgas\ ($\gtrsim$200,000 stars).  
We present a data-driven re-analysis of \Nspectra\ \rave\ spectra using 
\thecannon.  For red giants, we build our model using high-fidelity 
\apogee\ stellar parameters and abundances for stars that overlap 
with \rave.  For main-sequence and sub-giant stars, our model uses 
stellar parameters from the \epic.  We derive and validate 
effective temperature $\teff$, surface gravity $\logg$, and chemical 
abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni).  We 
report a total of \ReportedAbundances\ elemental abundances with a 
typical precision of 0.07~dex, a substantial improvement over previous 
\rave\ data releases.  The synthesis of \raveon\ and \tgas\ is the 
most powerful data set for chemo-dynamic analyses of the Milky Way ever produced.
\end{abstract}
